Bias in the Estimation of the Value of VRA over URA: A case of Mis-speficied Geographically Weighted Regression Models

### 2023-11-05 Writing/JAAEA/2ndRoundRevision/reply_to_reviewer_1.rmd

This comment clearly shows that this reviewer did not pay attention to our replies to his comments. In our reply to his comments, we clearly stated that the site-specific parameters are indeed spatially correlated. We also ensured that the coefficients on the linear and quadratic n-rates were constrained to be positive and negative. This is not a hard task. We share all the codes written in R on a publicly accessible repository. Anybody can check how this was done in our paper.

5. <span style = "color: blue;">Page 11, Line 206: was this random field generated once and then used for 1,000 MC iterations, or was the field generated for each MC iteration? What about the errors? What were the nugget, sill, etc., for each simulated parameter?  </span>

**Response**:

Site-specific parameters and errors were generated for each of the 1,000 Monte Carlo iterations, resulting in distinct spatial patterns of Economic Optimum Nitrogen Rate (EONR) for each simulation instance. However, the parameters of the variogram (such as nugget and sill) remain consistent across simulations, ensuring that the spatial dependence of the site-specific parameters is the same.

### 2023-11-11 Writing/manuscript_gwr.rmd
some changes made by Xiaofei

---
title: "Economic Evaluation of Mis-speficied Geographically Weighted Regression Models for Site-specific Nitrogen Management"
author:
  - Taro Mieno^[University of Nebraska Lincoln, tmieno2@unl.edu], Xiaofei Li^[Mississippi State University, xiaofei.li@msstate.edu], David S. Bullock^[University of Illinois, dsbulloc@illinois.edu]
output:
  officedown::rdocx_document:
    toc: false
    toc_depth: 1
    number_sections: true
    reference_docx: "word_template.docx"
    base_format: "bookdown::word_document2"
    plots:
      style: Normal
      align: center
      caption:
       style: Image Caption
       pre: "Figure "
       sep: ": "
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
       style: Table Caption
       pre: "Table "
       sep: ": "
bibliography: PA.bib
csl: field-crops-research.csl
abstract: ""
---

@@

In recent years, on-farm precision experimentation (OFPE) has gained traction with agricultural researchers and practitioners as a means of generating high-resolution spatial data to inform site-specific crop input management [@bullock2019data; @lacoste2021farm]. Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions with OFPE data.  Researchers recently have examined various methods, ranging from Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning techniques, including random forest [@krause2020random; @de2023predicting], convolutional neural network [@barbosa2020modeling], and causal forest [@kakimoto2022causal] approaches.  Among these, reported research on the GWR approach have generated special interest because GWR can be used to estimate site-specific yield-to-input relationships without costly spatial field and soil data.

@trevisan2021spatial demonstrated a method of providing site-specific management recommendations without such data. They estimated site-specific yield response functions by applying GWR techniques on OFPE data, and reported implausibly large results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and nitrogen (N) at optimal uniform rates instead of at the rates the farmers would have chosen if not participating in the research, and an additional potential gain of \$58 ha$^{-1}$ when changing from the optimal uniform application rate to optimal site-specific application rates. This might be seen as surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @harris2019simulation; @paez2011simulation; @da2016multiple] and also the much lower value of variable rate application (VRA)  management over uniform rate application (URA) management reported in previous studies [@bullock1998does; @koch2004economic; @thrikawala1999economic].

We hypothesize that the value of GWR reported by @trevisan2021spatial is a result of over-estimation bias. There are two key sources of bias in their approach. First, they assumed a quadratic functional form of yield response, even though a consensus has evolved in the academic literature that the quadratic-plateau functional form better represents the yield-nitrogen relationship. Second, as will be discussed in detail in the following section, their approach suffers from bias that is endemic to any study that tries to estimate the value of a statistical method in the OFPE context, which is that it is necessary because the true yield response function is unknowable and can only be estimated.

# Background: Estimation of Yield-to-input Response Relationships Using OFPE Data

## Conceptual Framework
OFPE can provide detailed as-applied input and yield data at dense resolutions over entire fields, which if well analyzed may provide valuable information that can improve site-specific input application recommendations [@bullock2019data; @lacoste2021farm]. Consider a yield response function $y = f(\textbf{x}, \textbf{c})$, where following @bullock2000agronomic, $\textbf{x}$ is a vector of input management variables and $\textbf{c}$ is a vector of spatial variables describing field and soil characteristics^[For simplicity, we suppress discussion of the need to bring variance in weather data into yield response estimation.  Obviously, generation and use of weather data is necessary to provide meaningful probabilistic analysis and input management advice.]. Letting a field site $i$ be defined as a contiguous area characterized uniformly by a value $\textbf{c}_i$ of the vector of field and soil characteristics, its *site-specific yield response function* is the reduced form of the field's yield response function created when the value of the vector of characteristics variables is set at the site's value, $\textbf{c}_i$:  $f_i(\textbf{x}) \equiv f(\textbf{x}, \textbf{c}_i)$.  This conceptualization suggests two methods of estimating a field's site-specific yield responses. The first is to estimate a "map" of the field characteristics, for example thought of as a set of the field's $n \geq 1$ sites' values of the characteristics vector: $\{\textbf{c}_1,\dots, \textbf{c}_n\}$.  With that map, regressing yield on $\textbf{x}$ and $\textbf{c}$ generates an estimated "field-specific" yield response function $\hat{f}(\textbf{x},\textbf{c})$. Estimates of site-specific yield response functions can then be obtained by inserting the value of the site's characteristic variables into the estimate of the field-specific response function: $\hat{f}_i(\textbf{x}) \equiv \hat{f}(\textbf{x},\textbf{c}_i)$. Alternatively, a site-specific yield response function might be estimated simply by taking (input rate, yield) data from points around a site of interest, and regressing yield on input application rates to attain the estimate $\hat{f}_i (\textbf{x})$. Stated roughly, using GWR takes the latter approach, which has the advantage of not needing a costly map of field characteristics values.

## Costs of Field Characteristics Data and the Appeal of GWR

On any given field, it is typical for many row crop farmers to pay for 1-ha (2.5-ac) grid soil sampling and chemical analysis every three or four years [@morris2018strengths]. The data are often used to derive fertilizer application recommendations, for example by applying comparatively simple formulas provided by university extension services (e.g., @culman2020tri). The expense of soil sampling and analysis is also driving development of new sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics, and the conversion of those data into recommended input application rate maps (usually called "prescriptions" or "$R_x$s"). For example, Trimble Agriculture's GreenSeeker and AgLeader's OptRx systems use optical sensors mounted on fertilizer application booms to digitally record vegetative index imagery as farm machinery is driven through fields during early crop growth stages. GreenSeeker then uses Oklahoma State University's Sensor-based N Rate Calculator to convert those data into recommended nitrogen fertilizer (N) $R_x$s. Veris Technologies manufactures sensor equipment that can be towed through fields to gather apparent electroconductivity (EC) data, which can be used to infer properties of soil content. The "decision tool" software FieldRevealTM allows users to upload EC data, elevation data, and vegetative index data, which FieldRevealTM's professional agronomists analyze to provide $R_x$s to farmers. FieldApex creates N $R_x$s using foliar vegetative index data from satellite imagery, and SlantRange uses drone imagery for similar purposes. But deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farming profitability remains in question [@gardner2021economic].

The appeal of GWR lies in its ability to estimate localized site-specific yield response functions without measuring these characteristics. It runs regressions locally at many points of the field to estimate yield response functions, where the locality is controlled by the bandwidth of the kernel function chosen by the researcher. Using OFPE data, @trevisan2021spatial assumed a quadratic yield response function, and reported large economic benefits associated with using GWR to generate site-specific seed and nitrogen rates recommendations. @rakshit2020 also estimated site-specific yield response functions by applying GWR to on-farm experiment data assuming a quadratic functional form of yield response.  But they did not calculate site-specific economically optimal nitrogen rates (EONRs), and so unlike @trevisan2021spatial, did not conduct economic analysis. @evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020, did not estimate site-specific economically optimal nitrogen rates.

@@

>>>>

---
title: "Bias in the Estimation of the Value of VRA over URA: A case of Mis-speficied Geographically Weighted Regression Models"
author:
  - Taro Mieno^[University of Nebraska Lincoln, tmieno2@unl.edu], Xiaofei Li^[Mississippi State University, xiaofei.li@msstate.edu], David S. Bullock^[University of Illinois, dsbulloc@illinois.edu]
output:
  officedown::rdocx_document:
    toc: false
    toc_depth: 1
    number_sections: true
    reference_docx: "word_template.docx"
    base_format: "bookdown::word_document2"
    plots:
      style: Normal
      align: center
      caption:
       style: Image Caption
       pre: "Figure "
       sep: ": "
    tables:
      style: Table
      layout: autofit
      width: 1.0
      caption:
       style: Table Caption
       pre: "Table "
       sep: ": "
bibliography: PA.bib
csl: field-crops-research.csl
abstract: ""
---

@@

While as-applied yield and input data are relatively easy to collect by modern farming machinery, gathering detailed soil characteristics data is often costly. On any given field, it is typical for many row crop farmers to pay for 1-ha (2.5-ac) grid soil sampling and chemical analysis every three or four years [@morris2018strengths]. The high expense of soil sampling and analysis is also driving development of new sensor technologies that gather data on site-specific field and crop characteristics or proxies of those characteristics, for example, mounted optical sensors for vegetative index (Trimble Agriculture's GreenSeeker and AgLeader's OptRx), towed soil sensor for electroconductivity data (Veris Technologies), etc. Those data are then converted into recommended input application rate maps (usually called "prescriptions" or "$R_x$s") by applying formulas provided by agricultural companies (e.g., FieldRevealTM, FieldApex) or university extension services (e.g., @culman2020tri). But deploying sophisticated sensors to gather field characteristics data is also costly, and the effects of their generation and use on farming profitability remains in question [@gardner2021economic].

In recent years, on-farm precision experimentation (OFPE) has gained traction with agricultural researchers and practitioners as a means of generating inexpensive, high-resolution yield and input trial data to inform site-specific crop input management [@bullock2019data; @lacoste2021farm]. Accompanying interest is surging among researchers in identifying efficient statistical methods to estimate site-specific yield response functions with OFPE data. Researchers recently have examined various methods, ranging from spatial econometrics [@anselin2004spatial; @liu2006site], Geographically Weighted Regression (GWR) [@rakshit2020; @evans2020assessment; @trevisan2021spatial] to machine learning techniques (suhc as random forest [@krause2020random; @de2023predicting], convolutional neural network [@barbosa2020modeling], and causal forest [@kakimoto2022causal]). Among these mehtods, however, most still require detailed soil sampling or field characteristics data together with the OFPE (yield, input) data for the site-specific estimation. The GWR model, on the other hand, runs a localized regression by taking only (yield, input) data from neighboring points around a site of interest, where the locality is controlled by the bandwidth of the kernel function chosen by the researcher. Therefore, it can estimate site-specific yield response functions without the costly soil and field characteristics data, and is appealing in OFPE data analysis.

@evans2020assessment explored using GWR with a linear model specification to detect low- and high-response areas, but like @rakshit2020, did not estimate site-specific economically optimal nitrogen rates.

@rakshit2020 also estimated site-specific yield response functions by applying GWR to on-farm experiment data assuming a quadratic functional form of yield response.  But they did not calculate site-specific economically optimal nitrogen rates (EONRs), and so unlike @trevisan2021spatial, did not conduct economic analysis.

Using OFPE data, @trevisan2021spatial assumed a quadratic yield response function, and reported large economic benefits associated with using GWR to generate site-specific seed and nitrogen rates recommendations.

@trevisan2021spatial demonstrated a method of providing site-specific management recommendations without such data. They estimated site-specific yield response functions by applying GWR techniques on OFPE data, and reported implausibly large results, estimating an average potential gain of \$65 ha$^{-1}$ from applying seed and nitrogen (N) at optimal uniform rates instead of at the rates the farmers would have chosen if not participating in the research, and an additional potential gain of \$58 ha$^{-1}$ when changing from the optimal uniform application rate to optimal site-specific application rates.

This might be seen as surprising given the often-reported poor statistical accuracy of GWR estimates [@griffith2008spatial; @harris2019simulation; @paez2011simulation; @da2016multiple] and also the much lower value of variable rate application (VRA) management over uniform rate application (URA) management reported in previous studies [@bullock1998does; @koch2004economic; @thrikawala1999economic].

* The central interest is the economic performance of GWR. We measure it by the profit improvement of GWR-based VRA over URA. We do not focus on statistical performance, as that is not the 
final goal

* Why we use simulation

@@

We hypothesize that the economic value of GWR reported by @trevisan2021spatial is a result of over-estimation bias. There are two key sources of bias in their approach. First, they assumed a quadratic functional form of yield response, even though a consensus has evolved in the academic literature that the quadratic-plateau functional form better represents the yield-nitrogen relationship. Second, as will be discussed in detail in the following section, their approach suffers from bias that is endemic to any study that tries to estimate the value of a statistical method in the OFPE context, which is that it is necessary because the true yield response function is unknowable and can only be estimated.

## Conceptual Framework: Estimation of Yield-to-input Response Relationships Using OFPE Data
OFPE can provide detailed as-applied input and yield data at dense resolutions over entire fields, which if well analyzed may provide valuable information that can improve site-specific input application recommendations [@bullock2019data; @lacoste2021farm]. Consider a yield response function $y = f(\textbf{x}, \textbf{c})$, where following @bullock2000agronomic, $\textbf{x}$ is a vector of input management variables and $\textbf{c}$ is a vector of spatial variables describing field and soil characteristics^[For simplicity, we suppress discussion of the need to bring variance in weather data into yield response estimation.  Obviously, generation and use of weather data is necessary to provide meaningful probabilistic analysis and input management advice.]. Letting a field site $i$ be defined as a contiguous area characterized uniformly by a value $\textbf{c}_i$ of the vector of field and soil characteristics, its *site-specific yield response function* is the reduced form of the field's yield response function created when the value of the vector of characteristics variables is set at the site's value, $\textbf{c}_i$:  $f_i(\textbf{x}) \equiv f(\textbf{x}, \textbf{c}_i)$.  This conceptualization suggests two methods of estimating a field's site-specific yield responses. The first is to estimate a "map" of the field characteristics, for example thought of as a set of the field's $n \geq 1$ sites' values of the characteristics vector: $\{\textbf{c}_1,\dots, \textbf{c}_n\}$.  With that map, regressing yield on $\textbf{x}$ and $\textbf{c}$ generates an estimated "field-specific" yield response function $\hat{f}(\textbf{x},\textbf{c})$. Estimates of site-specific yield response functions can then be obtained by inserting the value of the site's characteristic variables into the estimate of the field-specific response function: $\hat{f}_i(\textbf{x}) \equiv \hat{f}(\textbf{x},\textbf{c}_i)$. Alternatively, a site-specific yield response function might be estimated simply by taking (input rate, yield) data from points around a site of interest $i$, and regressing yield on input application rates to attain the estimate $\hat{f}_i (\textbf{x})$. Stated roughly, using GWR takes the latter approach, which has the advantage of not needing a costly map of field characteristics values.
